\documentclass{scrartcl}
\usepackage[a4paper, total={7in, 10in}]{geometry}
\usepackage{stmaryrd}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{color}
\usepackage{tikz}
\usepackage{MacrosArt}

\title{Generalized Morse theory for distance functions}

\author{José Lorgeré}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{flushleft}

\tableofcontents

\newpage
\setcounter{page}{1}

\section{Generalities on Lipschitz Functions}

\subsection{Lipschitz functions on manifolds and subdifferentials}

\quad For all the following, $M$ will denote a differentiable manifold of dimension $m$.
In this section, we generalize many definitions related to Lipschitz functions. We begin by
extending the definition of Lipschitz functions to functions on a manifold.

\begin{defi}
    A function $f : M \rightarrow \mathbb{R}^n$, where $M$ is a smooth manifold, is
    locally Lipschitz if for any chart $U \subset M$ and any compact $K \subset U$,
    there exists $C > 0$ such that, with the coordinates on $U$
    \[\forall x, y \in K, | f(x) - f(y) | \leq C |x - y| \]
\end{defi}

\quad Let $f : U \subset \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a Lipschitz function, where $U$ is
open. Rademacher's theorem, which states that $f$ is differentiable almost everywhere, will
allow us to generalize differentials to this setting.

\begin{defi}\cite{ClarkeImplicit}
    The subdifferential of $f$ at $x$, denoted by $\partial_x f$ is the convex hull of
    the linear maps $l$ obtained as
    \[ l = \lim_{i \rightarrow \infty} d_{x_i}f \]
    where $f$ is differentiable at each $x_i$ and $x_i \rightarrow x$.
\end{defi}

The subdifferential is then set valued. This set is always non empty and compact, $f$ being
Lipschitz bounds $df$ where it is defined.\newline
By \cite{ClarkeFirst}, we can exclude a set of measure $0$ from the possible values of $x_i$
without changing the definition.

% Example

\begin{prop}
    $\partial f$ is the smallest convex valued upper semi-continuous function containing
    $df$ whenever it is defined.
\end{prop}

\begin{proof}
    First, $\partial f$ is upper semi-continuous : by compactness, is suffices to
    show that for all $x \in U, \varepsilon > 0$, for $y$ sufficiently close to $x$.
    \[ \partial_y f \subset \partial_x f + B(0, \varepsilon)\]
    Assume for contradiction that there exists a sequence $x_i \rightarrow x$ such that for all $i$,
    $\partial_{x_i} f$ has an element out of $A := \partial_x f + \overline{B}(0, \varepsilon/2)$.
    $A$ being convex and closed, let $x'_i$ be such that $d_{x'_i} f$ is out of
    $A$, and such that $x'_i - x_i \rightarrow 0$. Up to extraction, $d_{x'_i} f$ converges to an element in 
    $\partial_x f$, so it enters $A$, contradiction.\newline \medskip
    The second part follow from $\partial f$ being a convex hull.
\end{proof}

\quad The subdifferential allows us to generalize the idea of regular and critical points, which will
be an important tool for generalizing Morse theory. The definition is as follows :

\begin{defi}
    A point $x \in U$ will be called critical if there exists some $l \in \partial_x f$
    not of maximal rank. $x$ will be called regular if it isn't critical.
\end{defi}

To extend these subdifferentiability notions to manifolds, one must guarantee that for all
charts, the definitions of $\partial f$ coincide. In this is the case, $\partial_x f$ is
a compact convex subset of $T_x^* M$. The following generalization of the chain rule
allows us to do that.

\begin{prop}[Subdifferential chain rule]
    Let $h : \mathbb{R}^n \rightarrow \mathbb{R}^k$ be a $C^1$ function. For $x \in U$ :
    \[ \partial_x (h \circ f) \subset d_{f(x)} h \circ \partial_x f \]
    If $h$ is a diffeomorpism, we have equality.
\end{prop}

\begin{proof}
    For the first part, because $f$ is differentiable a.e, it suffices to show that
    the leftwise term is an upper semi-continuous convex valued function that contains
    $d(h \circ f)$ whenever $df$ is defined. This follows from the definition of $\partial f$.
    \medskip \newline
    If $h$ is a diffeomorphism, then for $x \in U$ :
    \[ \partial_x f = \partial_x (h^{-1} \circ h \circ f)
        \subset d_{h \circ f (x)} h^{-1} \circ \partial_x (h \circ f) \subset \partial_x f \]
    so we have equalities, and the result follows.
\end{proof}

Although some important differentiablity related results can be obtained with locally
Lipschitz functions as we'll see, a general locally Lipschitz function can have some
pathological behaviours. As an example, it's subdifferential isn't in general a
topological submanifold of $M$ as illustrated by Figure ??. However, the functions we'll
study, for example continuous selections (see Section \ref{sec:ContSelec}) have much nicer
behaviour and we retrieve this property.

\subsection{Generalized differential theorems}

\quad We now consider the specific case of $f : U \subset \mathbb{R}^m \rightarrow \mathbb{R}^m$.
This section is devoted to proving generalizations by Clarke \cite{ClarkeImplicit} of the inverse function
theorem and the implicit function theorem for the case of Lipschitz functions.
\bigskip

\quad In this section, we norm the space of linear maps $\mathbb{R}^m \rightarrow \mathbb{R}^m$, which we denote
$\mathcal{L}(\mathbb{R}^n)$, with the operator norm $\| \cdot \|$ obtained from the norm used on
$\mathbb{R}^n$.

\begin{lem}\label{invfunlem}
    Assume $U$ is convex, and that there exists some closed convex set $C$ such that
    \begin{itemize}
        \item Every $l \in C$ is invertible.
        \item $\partial_x f \subset C$ for all $x \in U$
    \end{itemize}
    Then there exists some $\delta > 0$ such that for all $x, y \in U$ :
    \[ |f(x) - f(y)| \geq \delta |x - y| \]
\end{lem}

\begin{proof}
    Firstly, we set
    \[ \delta = \inf\left\{ |l(h)| \mid l \in C, h \in S \right\} \]
    where $S$ is the unit sphere in $\mathbb{R}^n$. $\delta > 0$ because all $l \in C$
    are invertible and $C \times S$ is closed.
    \medskip \newline
    Let $x, y \in U$ and assume $x \neq y$. Let $\pi$ be the plane perpendicular to $y - x$
    passing through $x$. $f$ being differentiable a.e, Fubini's theorem implies that
    for almost all $x' \in \pi$, $f$ is differentiable almost on the whole line passing
    through $x'$ and perpendicular to $\pi$ (i.e $f$ isn't differentiable on a subset of this line of
    one dimensional measure $0$).\newline
    Denoting $F : t \longmapsto f(x' + t(y-x))$, we have :
    \begin{equation}\label{eq:invfunlemeq}
        f(x' + y - x) - f(x') = \int_{0}^{1} F'(t) dt = \int_{0}^1 d_{x'+t(y-x)} f (y-x)dt
    \end{equation}
    Define the linear map
    \[ L = \int_0^1 d_{x'+t(y-x)} f dt \]
    $C$ being convex and closed, $L \in C$. Observe that the integral on the right of
    \eqref{eq:invfunlemeq} is just $L(y-x)$. So
    \[ |f(x'+y-x) - f(x')| \geq \delta |y-x| \]
    This inequality holds for almost all $x' \in \pi$, so by continuity of $f$, it holds for $x$
    and we get the desired result.
\end{proof}

\begin{theorem}[Lipschitz inverse function theorem]
    If $x_0$ is a regular point of $f$, then there exists $V, W$, neighbourhoods of $x_0$ and $f(x_0)$
    respectively, such that $f$ induces a bijection $f : V \rightarrow W$ where $f^{-1}$ is
    Lipschitz too.
\end{theorem}

\begin{proof}
    By compactness of $\partial_{x_0} f$, regularity of $x_0$, and the fact that the invertible
    linear maps form an open set, there exist some $\varepsilon > 0$ such that the set
    \[ C := \partial_{x_0} f + \overline{B}(0, \varepsilon) \]
    is composed only of invertible maps. By upper semi-continuity of $\partial f$, there is
    some $r > 0$ such that for $y \in B(x_0, r)$, $\partial f(y) \subset C$. We then
    apply Lemma \ref{invfunlem} with $U = B(x_0, r)$ and get a corresponding $\delta > 0$.
    \medskip \newline
    Set $V = B(x_0, r/2)$ and $W = f(V)$. We showed in particular that $f$ is injective on
    $\overline{V}$, by compactness $f : \overline{V} \rightarrow f(\overline{V})$ induces a homeomorphism. $W$
    is then open. The inequality we got with $\delta$ implies that $f^{-1}$ is $\frac{1}{\delta}$
    Lipschitz.
\end{proof}

From this theorem, follows the implicit function theorem for Lipschitz functions

\begin{theorem}
    Let $F : U \rightarrow \mathbb{R}^n$, where $U \subset \mathbb{R}^m \times \mathbb{R}^n$
    is open and $F$ is Lipschitz. Let $(x_0, y_0) \in U$ such that $F(x_0, y_0) = 0$
    and $y_0$ is a regular point of $y \mapsto F(x_0, y)$. Then there exist neighbourhoods
    $(x_0, y_0) \in W \subset U$, $x_0 \in V \subset R^m$ and a Lipschitz function
    $g : V \rightarrow \mathbb{R}^n$ such that
    \[ (x, y) \in W \text{ and } F(x, y) = 0 \Leftrightarrow x \in V \text{ and } y = g(x) \] 
\end{theorem}

The proof is almost the same as the usual implicit function theorem, where the continuity
of the differential is replaced by the semi continuity of $\partial F$.

\subsection{First Morse lemma for locally Lipschitz functions}

\quad The goal of this section is to use the generalized notion of critical points in order to
generalize the first Morse lemma to the case of locally Lipschitz functions. Fix $M$
an $m$-dimensional smooth manifold, $f : M \rightarrow \mathbb{R}$ a continuous function and
define for all $c \in \mathbb{R}$ the sublevel set of $f$ of value $c$ as
\[ M_c := f^{-1}(]-\infty, c]) \]
The classical first Morse lemma states that if $f$ is $C^1$, and there are no critical points
in $f^{-1}([a, b])$ (that we assume to be compact), then $M_b$ is diffeomorphic to $M_a$
and $M_a$ is a deformation retract of $M_b$. We extend this to locally Lipschitz functions,
following \cite{AgrachevContSelec}.
Note that in this setting $x$ is a critical point of $f$ iff $0 \in \partial_x f \subset T_x^*M$.

\begin{prop}\label{firstmorselem}
    Let $a < b \in \mathbb{R}$ such that $f^{-1}([a, b])$ is compact and free of critical points.
    Then $M_a$ is Lipschitz homeomorphic to $M_b$, $M_a$ is a deformation retract of $M_b$, the homotopy
    being locally Lipschitz.
\end{prop}

\begin{proof}
    We'll construct $V \in \operatorname*{Vec}(M)$ a smooth complete vector field on $M$
    such that, for all $x \in M$ such that $d_x f$ is defined :
    \begin{equation}\label{eq:Vsubgrad}
        d_x f (V(x)) \leq 0 \text{ and } d_x f(V(x)) \leq -1 \text{ if } x \in f^{-1}([a, b])
    \end{equation}
    Let $x \in f^{-1}([a, b])$. $x$ being regular and $\partial_x f$ convex, we find an affine hyperplane
    in $T^*_x M$ separating it from $0$. This gives us $v_x \in T_x M$ such that
    $\langle \partial_x f, v_x \rangle \leq -2$. By semi continuity, there exists
    an open neighbourhood $U_x$ of $x$ such that for all $y \in U_x$, $\langle \partial_y f, v_x \rangle \leq -1$.
    We choose this neighbourhood such that it has compact closure.
    \medskip \newline
    These $U_x$ cover $f^{-1}([a, b])$. Let $U_{x_1}, ..., U_{x_r}$ be a finite subcover, and let
    $\rho_1, ..., \rho_r$ be a partition of unity subordinated to this covering. We set
    \[\forall x \in M, V(x) = \sum_{i=1}^r \rho_i (x) v_{x_i} \]
    which indeed verifies \eqref{eq:Vsubgrad} : if $d_x f$ is defined, it is contained in $\partial_x f$,
    and $V$ is of compact support so it is complete.
    \medskip \newline
    Now observe that for $x \in f^{-1}([a, b])$, $t \mapsto f(e^{tV}x)$ is strictly decreasing.
    Denote by $t(x, s)$, $s \in [0, 1]$, the unique time such that $f(e^{t(x, s)V}x) = as + f(x)(1-s)$.
    The equation defining $t(x, s)$ is locally Lipschitz in $s, x$ and $t$, so by the Lipschitz implicit
    function theorem, $t$ is a locally Lipschitz function of $(x,s)$. The following homotopy
    verifies what we want

    \[ H : \begin{array}{cl}
        [0, 1] \times M_b &\longrightarrow M_b\\
        (s, x) &\longmapsto \left\{ \begin{array}{cl}
                e^{t(x,s)V}x & \text{ if } x \in f^{-1}([a, b])\\
                x & \text{ else}
        \end{array} \right.
    \end{array} \]

    We can similarly define $t'$ a locally Lipschitz function of $x$ such that
    $f(e^{t'(x)V}x) = b$ for $x$ in the orbit of some $y \in f^{-1}(b)$ by $V$. Denote
    $O$ the set of $x \in M$ that are in such orbits.
    The homeomorphism is then given by
    \[ \begin{array}{cl}
        M_b &\longrightarrow M_a\\
        x &\longmapsto \left\{ \begin{array}{cl}
                e^{t(e^{t'(x)V}x, 1)V}x & \text{ if } x \in O\\
                x &\text{ else}
            \end{array} \right.
    \end{array} \]
\end{proof}


\section{Morse theory of continuous selections}\label{sec:ContSelec}

\subsection{Definitions}

\quad We now restrict ourselves to continuous functions that are piecewise smooth with
finitely many pieces. Following (ref), we define those as continuous selections.

\begin{defi}
    A continuous function $f : M \rightarrow \mathbb{R}$ is a continuous selection if there
    exists $\varphi_1, ..., \varphi_n$ "regular" functions such that
    \[ \forall x \in M, f(x) \in \{ \varphi_1(x), ..., \varphi_n(x) \} \]
\end{defi}

The term "regular" is used loosely here to indicate that the $\varphi_i$ satisfy some
extra condition on top of being continuous. For what follows, we'll restrict ourselves
to continuous selections of smooth functions (but $C^2$ will suffice).
\medskip \newline
Note that a continous selection of locally Lipschitz functions is itself locally Lipschitz :
if $M$ is an open set of $\mathbb{R}^m$, and we assume that the functions $\varphi_i$ are
Lipschitz with constants $c_i$, then $f$ is Lipschitz with constant $\displaystyle \max_i c_i$.
Because smooth functions are locally Lipschitz, the functions we'll study will be too.
\medskip \newline
We can then relate $\partial f$ to the differentials of the $\varphi_i$. Indeed, a limit
of points of the form $d_x \varphi_i$ in $T^*M$ is of the same form. Define
the set of active indices at $x$,
\[ I(x) = \{ i \in \llbracket 1, n \rrbracket \mid \varphi_i(x) = f(x)\} \]
$\partial_x f$ is then the convex hull of some $d_x \varphi_i$, $i \in I(x)$.
It is possible that not all $d_x \varphi_i$ are used, if for example one of the functions isn't active
in a neighbourhood of $x$.
\bigskip

\quad We would like to define what it means for such a continuous selection to be Morse.
Let $f$ be a continuous selection of $\varphi_1, ..., \varphi_n$.
Following \cite{AgrachevContSelec}, we give three conditions for a function to be considered
Morse.
\begin{equation}\label{eq:morseCS1}
    \text{For all } i \neq j, \text{ the graphs of } \varphi_i \text{ and } \varphi_j \text{ are transversal.} \tag{C1}
\end{equation}
This condition has some important consequences :
for a non empty $I \subset \llbracket 1, n \rrbracket$, we define $W_I := \{ x \in M \mid I(x) = I \}$.
Condition \eqref{eq:morseCS1} implies that $W_I$ is a submanifold of $M$ of codimension
$|I|-1$ : the intersection of the graphs of $\varphi_i, i \in I$ is a submanifold of
$M \times \mathbb{R}$ of codimension $|I|$ and $W_I$ is the pre-image of this intersection
through the diffeomorphism $x \mapsto (x, \varphi_i(x))$, $i \in I$, with the codomain being
the graph of $\varphi_i$.
\medskip \newline
This transversality condition also implies that for $x \in M$,
the differentials $d_x \varphi_i$ are affinely independant where $i \in I(x)$.
In particular, $\partial_x f$ is a simplex with less than $|I(x)| - 1$ vertices.
\medskip \newline
Note that for all $I \subset \llbracket 1, n \rrbracket$, $f_{\mid W_I}$ is a smooth function.
This motivates the second condition
\begin{equation}\label{eq:morseCS2}
    \text{For all non empty } I \subset \llbracket 1, n \rrbracket, f_{\mid W_I} \text{ is Morse} \tag{C2}
\end{equation}
Consider $x \in M$ a critical point of $f$. Observe that $x$ must also be a critical point
of $f_{\mid W_{I(x)}}$. So
$\displaystyle T_x W_{I(x)} \subset \bigcap_{i \in I(x)} d_x \varphi_i$, but the converse can fail
if the $d_x \varphi_i$ are not linearly independant enough. The last condition fixes that
\begin{equation}\label{eq:morseCS3}
    \forall x \in M, \forall j \in I(x), (d_x \varphi_i)_{\substack{i \in I(x) \\ i \neq j}} \text{ are linearly independant} \tag{C3}
\end{equation}
Geometrically, this condition corresponds to requiring that $0$ is either outside or in the
interior of the simplex $\operatorname*{conv}\{ d_x \varphi_i \mid i \in I(x) \}$, but not on one of its faces.
Note (i think ??) that this condition can be relaxed by restricting it to the subset of $I(x)$ participating
in $\partial_x f$.
\bigskip

\quad A continuous selection $f$ is then called a Morse function if it verifies all three conditions.
Note that as in the smooth case, a generic continuous selection is Morse : \eqref{eq:morseCS1}
is a generic condition, any two functions can be slightly perturbed in order for their graphs
to be transversal, and any small perturbation of transversal graphs preserves transversality.
By genericity of smooth Morse functions, \eqref{eq:morseCS2} is also a generic condition. With
the geometric interpretation, we can also see that condition \eqref{eq:morseCS3} is generic.
% Morse example

\subsection{Normal form of a Morse continuous selection}

\quad We show here an equivalent of the second Morse lemma for the case of Morse continuous
selections. Noticing that $x \mapsto I(x)$ is upper semi-continuous and using the definitions
yields the following result.

\begin{lem}
    If $f : M \rightarrow \mathbb{R}$ is a Morse continuous selection, all its critical points
    are isolated.
\end{lem}

We'll then consider, up to restricting ourselves to a small enough chart,
that $f : \mathbb{R}^m \rightarrow \mathbb{R}$ is Morse and has no critical points other than $0$. We'll
write for shorthand $W := W_{I(0)}$, $k := |I(0)|-1$, $c := f(0)$, and assume that $I(0) = \llbracket 1, k+1 \rrbracket$.

\begin{theorem}
    If $0$ is a critical point of $f$, then there exists Lipschitz local coordinates around $0$,
    $\psi : \mathbb{R}^k \times \mathbb{R}^{m-k} \rightarrow U$ such that
    \[ \forall y \in \mathbb{R}^k, \forall z \in \mathbb{R}^{m-k}, f(\psi(y,z)) = \lambda(y) + q(z)\]
    where $\lambda$ is a continuous selection of $k+1$ linear functions, and $q$ is of the form
    \[ \forall z \in \mathbb{R}^{m-k}, q(z) = c -\sum_{i=1}^{\mu} z_i^2 + \sum_{i=\mu+1}^{m-k} z_i^2 \]
    with $0 \leq \mu \leq m-k$.
\end{theorem}

\begin{proof}
    We first restrict ourselves to $O$ a neighbourhood of $0$ such that $W$ can be considered
    rectified in some smooth coordinates i.e, $W \cap O = 0 \times \mathbb{R}^{m-k}$. We
    can also use the smooth Morse lemma to get $f(0, z) = q(z)$. For $(y, z) \in \mathbb{R}^m$,
    write $f^0(y, z) = f(y, z) - f(0, z)$. We will build for all $z$ close enough to $0$
    a locally invertible map $\psi_z : \mathbb{R}^k \rightarrow \mathbb{R}^k$ such that
    $\psi_z(0) = 0$ and for $y$ close enough to $0$, $f^0(\psi_z(y), z)$ is a continuous selection of
    linear maps independant of $z$.
    \medskip \newline
    For what follows we'll fix $z$ and omit it in the notations for convenience.
    We find a neighbourhood $U$ of $0 \in \mathbb{R}^k$ such that
    \begin{itemize}
        \item $U$ is connected.
        \item For all $y \in U$, $I(y) \subset \llbracket 1, k+1 \rrbracket$.
        \item For all $j \in \llbracket 1, k+1 \rrbracket$, the set $O_j$ of points in $U$
        such that $f(y) \neq \varphi_j(y)$ is open.
        \item There exists $\psi_j : U \rightarrow \mathbb{R}^k$ a diffeomorphism such that for all
        $i \neq j$, $\varphi_i(\psi_j(y)) = \varphi_i(0) + d_0 \varphi_i (y)$
        \item For all $y \neq 0$, $\psi_1(y), ..., \psi_{k+1}(y)$ are affinely independant.
    \end{itemize}
    We now want to combine these to take account of the possible intersections between the $O_j$.
    Our goal is to combine to $\psi_j$ together with a partition of unity
    $\mu_j : U \backslash\{0\} \rightarrow \mathbb{R}$ and set our final diffeomorphism to be
    \[ \psi(y) = \sum_{i = 1}^{k+1} \mu_i(y) \psi_i(y) \]
    Moreover, $\psi$ should take all active $\varphi_i$ to its affine approximation.\newline
    Let $\Omega \subset U$ be a maximal set on which this is possible.
    Assume there exists some non zero $y \in \Omega$ verifying that all of these exist at $y$.
    Let $j$ be such that $y \in O_j$. Set
    \[ F : \begin{array}{cl}
        U \times \mathbb{R}_{<1}^k &\longrightarrow \mathbb{R}^{k}\\
        (y,(\mu_i)_{i \neq j}) &\longmapsto \left( \varphi_i \left( \displaystyle \sum_{k \neq j} \mu_k \psi_k(y) + \left(1 - \sum_{k \neq j} \mu_k \right) \psi_j(y)\right) - \varphi_i(0) - d_0 \varphi_i(y)\right)_{i \neq j}
    \end{array}
    \]
    By assumption we have $F(y, (\mu_i(y)_{i \neq j})) = 0$. We can choose the $\psi_j$ to be
    affinely independant because the $d_0 \varphi_i$ are. Then, we use linear independance
    of the remaining $k$ $d_0 \varphi_i$ to show that the differential of $F$ along the $\mu$ coordinates
    is invertible. So by the implicit function theorem, there exists a neighbourhood of $y$
    on which $\mu_i$ $i \neq j$ can be extended, and because they sum up to $1$,
    we can also define $\mu_j$. So $\Omega$ is open in $U \backslash \{0\}$.
    \medskip \newline
    $\Omega$ is also closed in this set : assume there is a sequence $(y_r)$ in $\Omega$ converging
    to some non zero $y \in O_j$ for some $j$. By construction, the $\mu_i$ are bounded, so we can assume
    up to extraction that $\mu(y_r) \rightarrow \tilde{\mu}$. Then $F(y, (\tilde{\mu_i})_{i \neq j}) = 0$,
    and we again use the implicit function theorem to build functions $\tilde{\mu_i}$ on a ball
    around $y$. Now take any point $y' \in \Omega$ in this ball. The implicit function theorem
    states that the $\mu_i$ are the only functions that gives $0$ when fed into $F$ and defined on a certain
    ball around $y'$. $\tilde{\mu_i}$ also satisfies these conditions, so $\tilde{\mu_i}(y') = \mu_i(y')$,
    so we can extend $\mu_i$ to $y$, $y \in \Omega$.
    \medskip \newline
    Because $U \backslash \{0\}$ is connected, so $\Omega = U \backslash \{0\}$ because we can trivially
    define $\mu_i$ at a point where only one index isn't active. $\psi$ is then a local diffeomorphism
    using the fact that $d_0 \varphi_i \circ d_0 \psi = d_0 \varphi_i$ for all $i$.
    \medskip \newline
    We constructed for all $z$ close enough to $0$ to approximate $d_{(0, z)} \varphi_i$ by $d_0 \varphi_i$,
    $\psi_z$. They verify the following locally Lipschitz equation :
    $f(\psi_z(y), z) = \lambda(y) + q(z)$ where $\lambda$ is a continuous selection of $d_0 \varphi_i$.
    So $(z,y) \mapsto \psi_z(y)$ is locally Lipschitz.

\end{proof}



\end{flushleft}

\bibliographystyle{plain}
\bibliography{morseBib}

\end{document}